Pesticide exposure in small streams in Germany

### 2016-09-14 article.tex
added detection rates and mixtures

\subsection{Effect of precipitation on pesticide exposure}

The spatio-temporal intersection revealed that 5\% of the samples were taken at or after days with rainfall events greater than 10mm / day (Supplement, Figure S3).
Precipitation at the day before ($precip_{-1}$) sampling increased $\mu$ and also $\pi$ for nearly all modeled compounds. 
The effects were less pronounced ($\pi$) or not directed ($\mu$) for precipitation at the day of sampling ($precip_{0}$)(Figure \ref{fig:fig5}, top).

@@

\subsection{Pesticides in small water bodies}

\section{Discussion}
\subsection{Overview on the compiled dataset}
The compiled dataset of governmental monitoring data represents currently the most comprehensive one available for Germany.
Similar nationwide datasets have been compiled for the Netherlands \citep{vijver_spatial_2008}, Switzerland \citep{munz_pestizidmessungen_2011} and the United States (Water Quality Portal (WQP) \url{www.waterqualitydata.us}).
The data compiled and analysed here for Germany is of similar quantity and quality.

>>>>

\subsection{Effect of precipitation on pesticide exposure}
The spatio-temporal intersection revealed that 5\% of the samples were taken at or after days with rainfall events greater than 10mm / day (Supplement, Figure S3).
Precipitation at the day before ($precip_{-1}$) sampling increased $\mu$ and also $\pi$ for nearly all modeled compounds. 
The effects were less pronounced ($\pi$) or not directed ($\mu$) for precipitation at the day of sampling ($precip_{0}$)(Figure \ref{fig:fig5}, top).

@@

\subsection{Pesticides in small water bodies}
The dataset comprised 12,887 samples from 1313 small water bodies.
1173 samples (0.3\% of all and 5.6\% of samples with detects) RQ higher then 1 were observed.
Neonicotinoid Insecticides and Chlorpyrifos showed highest risk quotients (Figure \ref{fig:fig6}).
For Thiacloprid, Imidacloprid and Chlorpyrifos RAC was less than LOQ, therefore, all detections have a RQ \textgreater 1. 
The herbicides Nicosulfuron and Diflufenican, as well as the fungicide Dimoxystrobin showed also high exceedances of RQ (29.5/14.2/21.4 \% of all samples with detects).
Highest RQ were observed for Chlorpyrifos (max(RQ) = 244), Dimoxystrobin(max(RQ) = 117) and Isoproturon (max(RQ) = 80). 
Metabolites were most commonly detected in samples (Metazachlor sulfonix acid was in 82\% of all samples were it was analysed) (Supplement Figure S8)
Glyphosate was the compound with highest detection rates, followed by Boscalid and Isoproturon. 
However, only the latter showed RQ exceedances (Figure \ref{fig:fig6}).
In 44.8\% of samples more then one compound was quantified, with a maximum of 54 different compounds in one samples (supplemental figure S7).

\begin{figure}[h]
  \includegraphics[width=0.6\textwidth]{figure6.pdf}
  \caption{15 compounds with highest risk quotients in SWB. Non-detects are not shown due to the logarithmic axis. Numbers on the right give the percentage of RQ \textgreater 0 and total number of samples.
  }
  \label{fig:fig6}
\end{figure}

%% -------------------------------------------------------------------------
\section{Discussion}
\subsection{Overview on the compiled dataset}
The compiled dataset of governmental monitoring data represents currently the most comprehensive one available for Germany.
Similar nationwide datasets have been compiled for the Netherlands \citep{vijver_spatial_2008}, Switzerland \citep{munz_pestizidmessungen_2011} and the United States (Water Quality Portal (WQP) \url{www.waterqualitydata.us}).
The data compiled and analysed here for Germany is of similar quantity and quality.
